Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/10-introduction.tex
small fix in 2.3

The contributions of this article are the following.
% Contributions
\begin{enumerate*}[(i)]
    \item We review state of the art OCR and NER systems for historical documents (\cref{sec:related-work}).
    \item We introduce a new dataset suitable for OCR and NER evaluation (\cref{sec:dataset}).
    \item We measure the performance of three modern OCR systems on real data (\cref{sec:ocr-xp}).
    \item We evaluate modern NER approaches: their requirements in terms of training data, and the effects of pre-training (\cref{sec:ner-xp1}).
    \item We show that Transformed-based NER can benefit from pre-training and fine-tuning to improve its performance on noisy OCR (\cref{sec:ner-xp2}).
\end{enumerate*}

>>>>

The contributions of this article are as follows:
% Contributions
\begin{enumerate*}[(i)]
    \item We review state-of-the-art OCR and NER systems for historical documents (\cref{sec:related-work}).
    \item We introduce a new dataset suitable for OCR and NER evaluation (\cref{sec:dataset}).
    \item We measure the performance of three modern OCR systems on real data (\cref{sec:ocr-xp}).
    \item We evaluate modern NER approaches: their requirements in terms of training data, and the effects of pre-training (\cref{sec:ner-xp1}).
    \item We show that Transformed-based NER can benefit from pre-training and fine-tuning to improve its performance on noisy OCR (\cref{sec:ner-xp2}).
\end{enumerate*}

### 2022-01-20 src-latex/parts/20-related-work.tex
Fix US spelling.
small fix in 2.3

Based on those works, we chose to test three OCR systems, namely, Tesseract, \peroocr, and Kraken. We also adopt two deep-learning-based French language models, available in packaged software libraries, already trained for the NER task and that we can adapt to the domain of historical directories: SpaCy NLP pipelines and CamemBERT.
In \cref{sec:dataset}, we will explain the evaluation protocol used to assess the combined performance of these OCR and NER systems.

>>>>

Based on those works, we chose to test three OCR systems, namely, Tesseract, PERO OCR, and Kraken. We also adopt two deep-learning-based French language models, available in packaged software libraries, already trained for the NER task and that we can adapt to the domain of historical directories: SpaCy NLP pipelines and CamemBERT.
\Cref{fig.pipeline} depicts the evaluation protocol used to assess the combined performance of these OCR and NER systems.

### 2022-01-20 src-latex/parts/30-dataset.tex
small fix in 2.3

This section presents the historical sources that we selected and their contents. It also details the construction of the groundtruth dataset leveraged in our experiments and the metrics used to evaluate OCR and NER results.

\subsection{A selection of Paris trade directories from 1798 to 1854}
\label{sec:corpus}

@@

The simplified data extraction pipeline depicted in~\cref{fig.pipeline} processes the documents presented
in~\cref{sec:corpus}. First, the page layout extraction and entry segmentation are performed with a
semi-automated system and checked by a human. The resulting images, representing 8765 entries, are the inputs of a customizable two-stage pipeline.

>>>>

This section presents the historical sources that we selected and their contents. It also details the construction of the groundtruth dataset leveraged in our experiments and the metrics used.

\subsection{A selection of Paris trade directories from 1798 to 1854}

@@

The simplified data extraction pipeline depicted in~\cref{fig.pipeline} processes the documents presented
in~\cref{sec:dataset}. First, the page layout extraction and entry segmentation are performed with a
semi-automated system and checked by a human. The resulting images, representing 8765 entries, are the inputs of a customizable two-stage pipeline.
